Attractive people, Attractive jobs 

### 2024-04-20 paper/paper.qmd
Update paper.qmd

library(tidyverse)
library(palmerpenguins)
library(arrow)
library(ggplot2)
library(kableExtra)
library(knitr)

@@

set.seed(112)

cleaned_data |>
  select(higherstatusjob, lowerstatusjob, highlyattractive, lessattractive) |>
  slice_sample(n = 10) |>
  kable(
    col.names = c("higherstatusjob", "lowerstatusjob","highlyattractive", "lessattractive"),
  booktabs = TRUE
  )

@@

@@

```
## Gender Attractiveness Dataset

@@

cleaned_data|>
  slice_sample(n = 10) |>
  select(male, female, highlyattractive, lessattractive) |> 
  kable(
    col.names = c("male", "female", "highlyattractive", "lessattractive"),
  booktabs = TRUE
  )

@@

```{r}
#| message: false
#| echo: false
#| label: fig-physical
#| fig-cap: Physical attractives .vs employment (2023)
cleaned_data <- select(cleaned_data)

cleaned_data %>%
  ggplot(mapping = aes(x = highlyattractive, y = higherstatusjob)) +
  geom_bar(stat = "identity") +
  labs(
    title = "Highly Attractive vs. Higher Status Job in 2023",
    x = "Highly Attractive",
    y = "Employment"
  ) +
  scale_fill_manual(values = c("blue", "red")) +
  theme_classic()

@@

>>>>

library(tidyverse)
library(palmerpenguins)
library(arrow)
library(ggplot2)
library(kableExtra)
library(knitr)
library(dplyr)

@@

library(kableExtra)

cleaned_data |>
  slice_sample(n = 10) |>
  select(higherstatusjob, lowerstatusjob, highlyattractive, lessattractive) |>
  kable(
    col.names = c("higherstatusjob", "lowerstatusjob","highlyattractive", "lessattractive"),
  booktabs = TRUE
  )
```

@@

library(kableExtra)

@@

## Gender Attractiveness Dataset

@@

cleaned_data |>
  slice_sample(n = 10) |>
  select(male, female, highlyattractive, lessattractive) |>
  kable(
    col.names = c("male", "female", "highlyattractive", "lessattractive"),
  booktabs = TRUE
  )
slice

@@

```{r}
#| message: false
#| echo: false
#| label: fig-physical
#| fig-cap: Physical attractives .vs employment (2023)
library(ggplot2)

# Assuming 'cleaned_data' is your dataset
# You might need to adjust this code according to the structure of your dataset

# Select 100 random observations from the dataset
sampled_data <- cleaned_data[sample(nrow(cleaned_data), 100), ]

# Plot the bar graph
ggplot(sampled_data, aes(x = factor(highlyattractive), fill = factor(lowerstatusjob), y = 1)) +
  geom_bar(position = "stack", stat = "identity", color = "black") +
  facet_wrap(~ lessattractive, nrow = 1) +
  scale_fill_manual(values = c("blue", "red"), name = "Employment Status", labels = c("Higher Status Job", "Lower Status Job")) +
  labs(
    title = "Correlation between Attractiveness and Employment Status",
    x = "Attractiveness",
    y = "Count"
  ) +
  theme(axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())

@@

```{r}
sampled_data <- cleaned_data[sample(nrow(cleaned_data), 100), ]

convert_to_text <- function(x) {
  ifelse(x == 0, "less attractive", "attractive")
}

data <- data %>%
  mutate(across(where(~all(. %in% c(0, 1))), convert_to_text))

print(data)
```
